---
title: "Methods"
---

```{r methods-setup, include=FALSE}
library(readxl)
library(tidyverse)
library(knitr)
```

This section explains how the raw BLS files were loaded, cleaned, and used to
produce the results. Every code step is explained so the analysis is fully
reproducible.

## Loading the Data

The Excel files are formatted to read, not for R. They contain
descriptive title rows, multi-row column headers, and footnote markers embedded
in cell values. To handle this, we load each file with `col_names = FALSE`,
which prevents R from treating row 1 as column headers and instead assigns
generic names (`...1`, `...2`, etc.) that we rename manually.

```{r load, eval=FALSE}
library(readxl)
library(tidyverse)

# col_names = FALSE prevents R from using row 1 as headers.
# The BLS files have a title row and a label row before data begins,
# so letting R guess headers would break everything.
r8    <- read_excel(
  "case-and-demographic-characteristics-table-r8-2023-2024.xlsx",
  col_names = FALSE)

fatal <- read_excel("fatal.xlsx", col_names = FALSE)
```

## Cleaning R8

After loading, we drop the first two rows (the title and label rows) and rename
only the four columns we actually use. There are 23 columns in the file and we
ignore the rest.

```{r clean-r8, eval=FALSE}
# Drop the two header rows so data starts at row 1
r8_data <- r8[-c(1, 2), ]

# Rename only the columns we use.
# Column positions identified by inspecting the raw file:
#   col 1  = industry name
#   col 2  = NAICS code
#   col 3  = case type (DAFW, DART, or DJTR)
#   col 4  = total injury rate per 10,000 FTE workers
#   col 10 = falls, slips, trips rate per 10,000 FTE workers
names(r8_data)[1]  <- "industry"
names(r8_data)[2]  <- "naics"
names(r8_data)[3]  <- "case_type"
names(r8_data)[4]  <- "total_rate"
names(r8_data)[10] <- "fall_rate"
```

## Filtering to Target Sectors

Injury rates for three sectors were extracted from the SOII Table R8 using NAICS codes: manufacturing (31–33), finance and insurance (52), and professional, scientific, and technical services (54). Finance and insurance and professional services were selected as the most representative office-type sectors.

For each sector, the following are recorded:

- **Total DAFW rate** — overall nonfatal injury rate per 10,000 FTE workers
- **Fall-specific DAFW rate** — nonfatal fall injuries per 10,000 FTE workers
- **Fall share of total injuries** — falls as a percentage of all nonfatal injuries

DAFW (Days Away From Work) was chosen because it captures the most serious
nonfatal injuries (those severe enough to keep a worker completely away from
work).

```{r filter-r8, eval=FALSE}
# Filter to top-level NAICS sectors, DAFW case type only.
# Using the broadest NAICS code (e.g. "31-33" not "311") ensures we get
# the full sector average rather than a sub-industry figure.
mfg <- r8_data %>% filter(naics == "31-33", case_type == "DAFW")
fin <- r8_data %>% filter(naics == "52",    case_type == "DAFW")
pro <- r8_data %>% filter(naics == "54",    case_type == "DAFW")

# as.numeric() converts from character type (a side effect of col_names = FALSE).
# Suppressed cells shown as "-" in the BLS table will become NA here.
mfg_total <- as.numeric(mfg$total_rate[1])
mfg_falls <- as.numeric(mfg$fall_rate[1])
fin_total  <- as.numeric(fin$total_rate[1])
fin_falls  <- as.numeric(fin$fall_rate[1])
pro_total  <- as.numeric(pro$total_rate[1])
pro_falls  <- as.numeric(pro$fall_rate[1])

# Derived measure: falls as a percentage of all nonfatal injuries per sector
mfg_fall_share <- round(mfg_falls / mfg_total * 100, 1)
fin_fall_share  <- round(fin_falls  / fin_total  * 100, 1)
pro_fall_share  <- round(pro_falls  / pro_total  * 100, 1)
```

## Extracting Fatal Data

The CFOI file has a different structure from R8. Rather than filtering by a
code column, we extract rows by their verified position in the file, identified
by inspecting the raw data directly. Column 3 contains total fatal injuries;
column 7 contains fatal falls, slips, and trips.

```{r clean-fatal, eval=FALSE}
# Convert to data frame for row-based indexing
fatal_df <- as.data.frame(fatal)

# Row positions verified from raw file inspection:
# Row 143 = Manufacturing (NAICS 31-33)
# Row 453 = Finance and insurance (NAICS 52)
# Row 488 = Professional, scientific, and technical services (NAICS 54)
mfg_fatal_total <- as.numeric(fatal_df[143, 3])
mfg_fatal_falls <- as.numeric(fatal_df[143, 7])
fin_fatal_total <- as.numeric(fatal_df[453, 3])
fin_fatal_falls <- as.numeric(fatal_df[453, 7])
pro_fatal_total <- as.numeric(fatal_df[488, 3])
pro_fatal_falls <- as.numeric(fatal_df[488, 7])

#Fatal injury counts were taken directly from CFOI Table A-1. Fall share of deaths are calculated by dividing fatal falls by total sector deaths.
mfg_fall_pct <- round(mfg_fatal_falls / mfg_fatal_total * 100, 1)
fin_fall_pct  <- round(fin_fatal_falls  / fin_fatal_total  * 100, 1)
pro_fall_pct  <- round(pro_fatal_falls  / pro_fatal_total  * 100, 1)
```

No statistical tests were conducted. Both the SOII and CFOI represent population-level estimates, so the observed differences between sectors reflect real differences rather than sampling error.
