---
title: "Results"
---

```{r results-setup, include=FALSE}
library(readxl)
library(tidyverse)
library(knitr)

r8_data <- read_excel(
  "case-and-demographic-characteristics-table-r8-2023-2024.xlsx",
  col_names = FALSE
)[-c(1, 2), ]

names(r8_data)[1]  <- "industry"
names(r8_data)[2]  <- "naics"
names(r8_data)[3]  <- "case_type"
names(r8_data)[4]  <- "total_rate"
names(r8_data)[10] <- "fall_rate"

mfg <- r8_data |> filter(naics == "31-33", case_type == "DAFW")
fin <- r8_data |> filter(naics == "52",    case_type == "DAFW")
pro <- r8_data |> filter(naics == "54",    case_type == "DAFW")

mfg_total <- as.numeric(mfg$total_rate[1])
mfg_falls <- as.numeric(mfg$fall_rate[1])
fin_total  <- as.numeric(fin$total_rate[1])
fin_falls  <- as.numeric(fin$fall_rate[1])
pro_total  <- as.numeric(pro$total_rate[1])
pro_falls  <- as.numeric(pro$fall_rate[1])

mfg_fall_share <- round(mfg_falls / mfg_total * 100, 1)
fin_fall_share <- round(fin_falls / fin_total  * 100, 1)
pro_fall_share <- round(pro_falls / pro_total  * 100, 1)

mfg_fatal_total <- 353; mfg_fatal_falls <- 52
fin_fatal_total <- 18;  fin_fatal_falls <- 6
pro_fatal_total <- 65;  pro_fatal_falls <- 10

mfg_fall_pct <- round(mfg_fatal_falls / mfg_fatal_total * 100, 1)
fin_fall_pct <- round(fin_fatal_falls / fin_fatal_total * 100, 1)
pro_fall_pct <- round(pro_fatal_falls / pro_fatal_total * 100, 1)

# Fatal: CFOI 
fatal_df <- as.data.frame(read_excel("fatal.xlsx", col_names = FALSE))

mfg_fatal_total <- as.numeric(fatal_df[143, 3])
mfg_fatal_falls <- as.numeric(fatal_df[143, 7])
fin_fatal_total <- as.numeric(fatal_df[453, 3])
fin_fatal_falls <- as.numeric(fatal_df[453, 7])
pro_fatal_total <- as.numeric(fatal_df[488, 3])
pro_fatal_falls <- as.numeric(fatal_df[488, 7])

mfg_fall_pct <- round(mfg_fatal_falls / mfg_fatal_total * 100, 1)
fin_fall_pct  <- round(fin_fatal_falls  / fin_fatal_total  * 100, 1)
pro_fall_pct  <- round(pro_fatal_falls  / pro_fatal_total  * 100, 1)
```


# Primary Analysis: Nonfatal Injury Rates (R8)

As shown in @tbl-nonfatal, manufacturing workers experienced a total nonfatal injury rate of `r mfg_total` per 10,000 FTE workers — roughly `r round(mfg_total / fin_total, 0)` times higher than the rate in finance and insurance (`r fin_total`) and `r round(mfg_total / pro_total, 1)` times higher than professional services (`r pro_total`).

```{r}
#| label: tbl-nonfatal
#| tbl-cap: "Nonfatal injury rates per 10,000 FTE workers by sector (SOII, 2023–2024)"
#| echo: false

tibble(
  Sector = c("Manufacturing", "Finance & Insurance", "Professional Services"),
  `Total Rate` = c(mfg_total, fin_total, pro_total),
  `Fall Rate` = c(mfg_falls, fin_falls, pro_falls),
  `Falls as % of Total` = c(
    paste0(mfg_fall_share, "%"),
    paste0(fin_fall_share, "%"),
    paste0(pro_fall_share, "%")
  )
) |>
  kable()
```

### Fall-Specific Risk

While manufacturing workers have more falls in absolute terms, falls represent a much larger *proportion* of injuries in office sectors. As seen in @tbl-nonfatal, falls account for `r fin_fall_share`% of all nonfatal injuries in finance and insurance, and `r pro_fall_share`% in professional services — compared to just `r mfg_fall_share`% in manufacturing.

::: {.callout-important}
## Key Finding
In office environments, falls are the dominant injury type and account for
over a third of all nonfatal injuries. In manufacturing, falls are just one type of injury. This means fall prevention deserves more attention in office safety programs.
:::


## Secondary Analysis: Fatal Injuries (CFOI)


@tbl-fatal shows fatal injury counts and fall-related deaths by sector in 2024. Manufacturing had `r mfg_fatal_total` workplace deaths, with `r mfg_fatal_falls` (`r mfg_fall_pct`%) caused by falls. Finance and insurance had `r fin_fatal_total` total deaths, with `r fin_fatal_falls` (`r fin_fall_pct`%) from falls. Professional services had `r pro_fatal_total` deaths, with `r pro_fatal_falls` (`r pro_fall_pct`%) from falls.

```{r}
#| label: tbl-fatal
#| tbl-cap: "Fatal occupational injuries by sector (CFOI, 2024)"
#| echo: false

tibble(
  Sector = c("Manufacturing", "Finance & Insurance", "Professional Services"),
  `Total Deaths` = c(mfg_fatal_total, fin_fatal_total, pro_fatal_total),
  `Deaths from Falls` = c(mfg_fatal_falls, fin_fatal_falls, pro_fatal_falls),
  `Falls as % of Deaths` = c(
    paste0(mfg_fall_pct, "%"),
    paste0(fin_fall_pct, "%"),
    paste0(pro_fall_pct, "%")
  )
) |>
  kable()
```

The pattern is consistent across both nonfatal and fatal data: falls are proportionally far more significant in office sectors than in manufacturing.

## Summary of Key Comparisons

@tbl-summary provides a side-by-side comparison of the fall share of injuries across both nonfatal and fatal measures.

```{r}
#| label: tbl-summary
#| tbl-cap: "Falls as a share of total injuries — nonfatal and fatal comparison"
#| echo: false

tibble(
  Sector = c("Manufacturing", "Finance & Insurance", "Professional Services"),
  `Falls: % of Nonfatal Injuries` = c(
    paste0(mfg_fall_share, "%"),
    paste0(fin_fall_share, "%"),
    paste0(pro_fall_share, "%")
  ),
  `Falls: % of Deaths` = c(
    paste0(mfg_fall_pct, "%"),
    paste0(fin_fall_pct, "%"),
    paste0(pro_fall_pct, "%")
  )
) |>
  kable()
```

::: {.callout-note}
## Consistency Across Sources
The fall share is higher in office sectors than in manufacturing in both the
nonfatal data (R8) and the fatal data (CFOI). This consistency across two
independent datasets.
:::
