---
title: "Results"
---

```{r results-setup, include=FALSE}
library(readxl)
library(tidyverse)
library(knitr)

r8_data <- read_excel(
  "case-and-demographic-characteristics-table-r8-2023-2024.xlsx",
  col_names = FALSE
)[-c(1, 2), ]

names(r8_data)[1]  <- "industry"
names(r8_data)[2]  <- "naics"
names(r8_data)[3]  <- "case_type"
names(r8_data)[4]  <- "total_rate"
names(r8_data)[10] <- "fall_rate"

mfg <- r8_data |> filter(naics == "31-33", case_type == "DAFW")
fin <- r8_data |> filter(naics == "52",    case_type == "DAFW")
pro <- r8_data |> filter(naics == "54",    case_type == "DAFW")

mfg_total <- as.numeric(mfg$total_rate[1])
mfg_falls <- as.numeric(mfg$fall_rate[1])
fin_total  <- as.numeric(fin$total_rate[1])
fin_falls  <- as.numeric(fin$fall_rate[1])
pro_total  <- as.numeric(pro$total_rate[1])
pro_falls  <- as.numeric(pro$fall_rate[1])

mfg_fall_share <- round(mfg_falls / mfg_total * 100, 1)
fin_fall_share <- round(fin_falls / fin_total  * 100, 1)
pro_fall_share <- round(pro_falls / pro_total  * 100, 1)

mfg_fatal_total <- 353; mfg_fatal_falls <- 52
fin_fatal_total <- 18;  fin_fatal_falls <- 6
pro_fatal_total <- 65;  pro_fatal_falls <- 10

mfg_fall_pct <- round(mfg_fatal_falls / mfg_fatal_total * 100, 1)
fin_fall_pct <- round(fin_fatal_falls / fin_fatal_total * 100, 1)
pro_fall_pct <- round(pro_fatal_falls / pro_fatal_total * 100, 1)

# Fatal: CFOI 
fatal_df <- as.data.frame(read_excel("fatal.xlsx", col_names = FALSE))

mfg_fatal_total <- as.numeric(fatal_df[143, 3])
mfg_fatal_falls <- as.numeric(fatal_df[143, 7])
fin_fatal_total <- as.numeric(fatal_df[453, 3])
fin_fatal_falls <- as.numeric(fatal_df[453, 7])
pro_fatal_total <- as.numeric(fatal_df[488, 3])
pro_fatal_falls <- as.numeric(fatal_df[488, 7])

mfg_fall_pct <- round(mfg_fatal_falls / mfg_fatal_total * 100, 1)
fin_fall_pct  <- round(fin_fatal_falls  / fin_fatal_total  * 100, 1)
pro_fall_pct  <- round(pro_fatal_falls  / pro_fatal_total  * 100, 1)
```


## Primary Analysis: Nonfatal Injury Rates (R8)

As shown in @tbl-nonfatal, manufacturing workers experienced a total nonfatal injury rate of `r mfg_total` per 10,000 FTE workers — roughly `r round(mfg_total / fin_total, 0)` times higher than the rate in finance and insurance (`r fin_total`) and `r round(mfg_total / pro_total, 1)` times higher than professional services (`r pro_total`).

```{r}
#| label: tbl-nonfatal
#| tbl-cap: "Nonfatal injury rates per 10,000 FTE workers by sector (SOII, 2023–2024)"
#| echo: false

tibble(
  Sector = c("Manufacturing", "Finance & Insurance", "Professional Services"),
  `Total Rate` = c(mfg_total, fin_total, pro_total),
  `Fall Rate` = c(mfg_falls, fin_falls, pro_falls),
  `Falls as % of Total` = c(
    paste0(mfg_fall_share, "%"),
    paste0(fin_fall_share, "%"),
    paste0(pro_fall_share, "%")
  )
) |>
  kable()
```

### Fall-Specific Risk

While manufacturing workers have more falls in absolute terms, falls represent a much larger *proportion* of injuries in office sectors. As seen in @tbl-nonfatal, falls account for `r fin_fall_share`% of all nonfatal injuries in finance and insurance, and `r pro_fall_share`% in professional services — compared to just `r mfg_fall_share`% in manufacturing.

::: {.callout-important}
## Key Finding
In office environments, falls are the dominant injury type and account for
over a third of all nonfatal injuries. In manufacturing, falls are just one type of injury. This means fall prevention deserves more attention in office safety programs.
:::

```{r,warning=FALSE}
#| label: fig-pictogram
#| fig-cap: "Each square represents 1 out of a 100 injured workers. Red squares were injured in a fall."
#| echo: false

library(ggplot2)

pictogram <- function(fall_share, title) {
  df <- expand.grid(x = 1:10, y = 1:10)
  df$fill <- c(
    rep("Fall injury", round(fall_share)),
    rep("Other", 100 - round(fall_share))
  )
  
  ggplot(df, aes(x = x, y = y, fill = fill)) +
    geom_tile(color = "white", size = 0.5) +
    scale_fill_manual(
      values = c("Fall injury" = "red", "Other" = "lightblue"),
      name = NULL
    ) +
    labs(title = title) +
    theme_void() +
    theme(
      legend.position = "bottom"
    )
}

p1 <- pictogram(mfg_fall_share, 
                     paste0("Manufacturing ", mfg_fall_share,"%"))
p2 <- pictogram(fin_fall_share, 
                     paste0("Finance & Insurance ", fin_fall_share, "%"))
p3 <- pictogram(pro_fall_share, 
                     paste0("Professional Services ", pro_fall_share, "%"))

library(patchwork)
p1 + p2 + p3
```

## Secondary Analysis: Fatal Injuries (CFOI)


@tbl-fatal shows fatal injury counts and fall-related deaths by sector in 2024. Manufacturing had `r mfg_fatal_total` workplace deaths, with `r mfg_fatal_falls` (`r mfg_fall_pct`%) caused by falls. Finance and insurance had `r fin_fatal_total` total deaths, with `r fin_fatal_falls` (`r fin_fall_pct`%) from falls. Professional services had `r pro_fatal_total` deaths, with `r pro_fatal_falls` (`r pro_fall_pct`%) from falls.

```{r, warning=FALSE}
#| label: tbl-fatal
#| tbl-cap: "Fatal occupational injuries by sector (CFOI, 2024)"
#| echo: false

tibble(
  Sector = c("Manufacturing", "Finance & Insurance", "Professional Services"),
  `Total Deaths` = c(mfg_fatal_total, fin_fatal_total, pro_fatal_total),
  `Deaths from Falls` = c(mfg_fatal_falls, fin_fatal_falls, pro_fatal_falls),
  `Falls as % of Deaths` = c(
    paste0(mfg_fall_pct, "%"),
    paste0(fin_fall_pct, "%"),
    paste0(pro_fall_pct, "%")
  )
) |>
  kable()
```

The pattern is consistent across both nonfatal and fatal data: falls are proportionally more significant in office sectors than in manufacturing.

::: {.callout-note}
### Summary Across Both Datasets

| Sector | Falls % of Nonfatal | Falls % of Deaths |
|---|---|---|
| Manufacturing | `r mfg_fall_share`% | `r mfg_fall_pct`% |
| Finance & Insurance | `r fin_fall_share`% | `r fin_fall_pct`% |
| Professional Services | `r pro_fall_share`% | `r pro_fall_pct`% |

Falls are proportionally more prevelant in office sectors across both datasets.

:::


