---
title: "Ai-use"
format: html
---

I used AI to help me form comments for my methods section, comments were similar to the ones submitted in the draft. I used this when I was unaware what the proper notation/tone was for commenting on code in a business level report and was going to show the code of the methods section. After feedback that my code should not be included in the report, I have deleted those comments, however, I have still included the model, prompts, and outputs, and changed version below.

Model: Chat GPT Plus 

Prompt: "Can you add comments to this code that would be considered professional and appropriate for a "business report" here is the code, just add comments:

```{r methods-setup, include=FALSE}
library(readxl)
library(tidyverse)
library(knitr)
```

```{r load, eval=FALSE}
library(readxl)
library(tidyverse)


r8    <- read_excel(
  "case-and-demographic-characteristics-table-r8-2023-2024.xlsx",
  col_names = FALSE)

fatal <- read_excel("fatal.xlsx", col_names = FALSE)
```

```{r clean-r8, eval=FALSE}

r8_data <- r8[-c(1, 2), ]


names(r8_data)[1]  <- "industry"
names(r8_data)[2]  <- "naics"
names(r8_data)[3]  <- "case_type"
names(r8_data)[4]  <- "total_rate"
names(r8_data)[10] <- "fall_rate"
```

```{r filter-r8, eval=FALSE}

mfg <- r8_data %>% filter(naics == "31-33", case_type == "DAFW")
fin <- r8_data %>% filter(naics == "52",    case_type == "DAFW")
pro <- r8_data %>% filter(naics == "54",    case_type == "DAFW")


mfg_total <- as.numeric(mfg$total_rate[1])
mfg_falls <- as.numeric(mfg$fall_rate[1])
fin_total  <- as.numeric(fin$total_rate[1])
fin_falls  <- as.numeric(fin$fall_rate[1])
pro_total  <- as.numeric(pro$total_rate[1])
pro_falls  <- as.numeric(pro$fall_rate[1])


mfg_fall_share <- round(mfg_falls / mfg_total * 100, 1)
fin_fall_share  <- round(fin_falls  / fin_total  * 100, 1)
pro_fall_share  <- round(pro_falls  / pro_total  * 100, 1)
```

```{r clean-fatal, eval=FALSE}

fatal_df <- as.data.frame(fatal)

mfg_fatal_total <- as.numeric(fatal_df[143, 3])
mfg_fatal_falls <- as.numeric(fatal_df[143, 7])
fin_fatal_total <- as.numeric(fatal_df[453, 3])
fin_fatal_falls <- as.numeric(fatal_df[453, 7])
pro_fatal_total <- as.numeric(fatal_df[488, 3])
pro_fatal_falls <- as.numeric(fatal_df[488, 7])


mfg_fall_pct <- round(mfg_fatal_falls / mfg_fatal_total * 100, 1)
fin_fall_pct  <- round(fin_fatal_falls  / fin_fatal_total  * 100, 1)
pro_fall_pct  <- round(pro_fatal_falls  / pro_fatal_total  * 100, 1)
```

```{r clean-r8, eval=FALSE}

r8_data <- r8[-c(1, 2), ]


names(r8_data)[1]  <- "industry"
names(r8_data)[2]  <- "naics"
names(r8_data)[3]  <- "case_type"
names(r8_data)[4]  <- "total_rate"
names(r8_data)[10] <- "fall_rate"
```

```{r filter-r8, eval=FALSE}

mfg <- r8_data %>% filter(naics == "31-33", case_type == "DAFW")
fin <- r8_data %>% filter(naics == "52",    case_type == "DAFW")
pro <- r8_data %>% filter(naics == "54",    case_type == "DAFW")


mfg_total <- as.numeric(mfg$total_rate[1])
mfg_falls <- as.numeric(mfg$fall_rate[1])
fin_total  <- as.numeric(fin$total_rate[1])
fin_falls  <- as.numeric(fin$fall_rate[1])
pro_total  <- as.numeric(pro$total_rate[1])
pro_falls  <- as.numeric(pro$fall_rate[1])


mfg_fall_share <- round(mfg_falls / mfg_total * 100, 1)
fin_fall_share  <- round(fin_falls  / fin_total  * 100, 1)
pro_fall_share  <- round(pro_falls  / pro_total  * 100, 1)
```

```{r clean-fatal, eval=FALSE}

fatal_df <- as.data.frame(fatal)


mfg_fatal_total <- as.numeric(fatal_df[143, 3])
mfg_fatal_falls <- as.numeric(fatal_df[143, 7])
fin_fatal_total <- as.numeric(fatal_df[453, 3])
fin_fatal_falls <- as.numeric(fatal_df[453, 7])
pro_fatal_total <- as.numeric(fatal_df[488, 3])
pro_fatal_falls <- as.numeric(fatal_df[488, 7])


mfg_fall_pct <- round(mfg_fatal_falls / mfg_fatal_total * 100, 1)
fin_fall_pct  <- round(fin_fatal_falls  / fin_fatal_total  * 100, 1)
pro_fall_pct  <- round(pro_fatal_falls  / pro_fatal_total  * 100, 1)
```



Output:

```{r}
library(readxl)
library(tidyverse)

# Ingest SOII Table R8 and CFOI datasets as raw, unstructured tables.
# col_names = FALSE enforces positional indexing by preventing implicit header parsing,
# which would otherwise mis-specify variable names due to multi-line headers and metadata rows.
# All columns are therefore imported as unnamed character vectors for controlled post-processing.
r8 <- read_excel(
  "case-and-demographic-characteristics-table-r8-2023-2024.xlsx",
  col_names = FALSE
)

fatal <- read_excel(
  "fatal.xlsx",
  col_names = FALSE
)
# Remove leading non-data rows (metadata + header rows) to align row indices
# with observational units; ensures row 1 corresponds to the first valid record
r8_data <- r8[-c(1, 2), ]

# Perform partial schema definition via positional column renaming.
# Column indices are fixed based on deterministic structure of the source file.
# Only analytically relevant variables are materialized; remaining columns are ignored.
names(r8_data)[1]  <- "industry"     # Nominal industry descriptor
names(r8_data)[2]  <- "naics"        # Categorical NAICS code (sector-level aggregation)
names(r8_data)[3]  <- "case_type"    # Injury classification indicator
names(r8_data)[4]  <- "total_rate"   # Incidence rate (total injuries per 10,000 FTE)
names(r8_data)[10] <- "fall_rate"    # Incidence rate (falls per 10,000 FTE)
# Restrict dataset to sector-level aggregates using top-level NAICS codes.
# Filtering on case_type == "DAFW" isolates higher-severity nonfatal injuries,
# operationalized as incidents resulting in ≥1 full day away from work.
# This produces one-row subsets representing sector-level summary statistics.
mfg <- r8_data %>% filter(naics == "31-33", case_type == "DAFW")
fin <- r8_data %>% filter(naics == "52",    case_type == "DAFW")
pro <- r8_data %>% filter(naics == "54",    case_type == "DAFW")

# Extract scalar values from single-row tibbles via positional indexing.
# Type coercion (character → numeric) is required due to initial raw import.
# Non-numeric placeholders (e.g., suppression symbols) propagate as NA under coercion.
mfg_total <- as.numeric(mfg$total_rate[1])
mfg_falls <- as.numeric(mfg$fall_rate[1])

fin_total <- as.numeric(fin$total_rate[1])
fin_falls <- as.numeric(fin$fall_rate[1])

pro_total <- as.numeric(pro$total_rate[1])
pro_falls <- as.numeric(pro$fall_rate[1])

# Construct derived proportion: fall-related incidence relative to total incidence.
# Computation is vectorized at scalar level and scaled to percentage form.
mfg_fall_share <- round((mfg_falls / mfg_total) * 100, 1)
fin_fall_share <- round((fin_falls / fin_total) * 100, 1)
pro_fall_share <- round((pro_falls / pro_total) * 100, 1)
# Convert tibble to base data.frame to ensure compatibility with explicit
# integer-based row/column indexing (i,j notation)
fatal_df <- as.data.frame(fatal)

# Extract sector-level fatality counts via fixed row indices.
# Row mappings correspond to sector aggregates identified through deterministic
# inspection of the source file structure (non-relational layout).
# Column 3 = total fatalities; Column 7 = fall-related fatalities.
mfg_fatal_total <- as.numeric(fatal_df[143, 3])
mfg_fatal_falls <- as.numeric(fatal_df[143, 7])

fin_fatal_total <- as.numeric(fatal_df[453, 3])
fin_fatal_falls <- as.numeric(fatal_df[453, 7])

pro_fatal_total <- as.numeric(fatal_df[488, 3])
pro_fatal_falls <- as.numeric(fatal_df[488, 7])

# Compute conditional proportion of fatalities attributable to falls within sector.
# Results are normalized and expressed as percentages with one-decimal precision.
mfg_fall_pct <- round((mfg_fatal_falls / mfg_fatal_total) * 100, 1)
fin_fall_pct <- round((fin_fatal_falls / fin_fatal_total) * 100, 1)
pro_fall_pct <- round((pro_fatal_falls / pro_fatal_total) * 100, 1)
```





Changed to:
```{r methods-setup, include=FALSE}
library(readxl)
library(tidyverse)
library(knitr)
```

```{r load, eval=FALSE}
library(readxl)
library(tidyverse)

# col_names = FALSE prevents R from using row 1 as headers.
# The BLS files have a title row and a label row before data begins,
# so letting R guess headers would break everything.
r8    <- read_excel(
  "case-and-demographic-characteristics-table-r8-2023-2024.xlsx",
  col_names = FALSE)

fatal <- read_excel("fatal.xlsx", col_names = FALSE)
```

```{r clean-r8, eval=FALSE}
# Drop the two header rows so data starts at row 1
r8_data <- r8[-c(1, 2), ]

# Rename only the columns we use.
# Column positions identified by inspecting the raw file:
#   col 1  = industry name
#   col 2  = NAICS code
#   col 3  = case type (DAFW, DART, or DJTR)
#   col 4  = total injury rate per 10,000 FTE workers
#   col 10 = falls, slips, trips rate per 10,000 FTE workers
names(r8_data)[1]  <- "industry"
names(r8_data)[2]  <- "naics"
names(r8_data)[3]  <- "case_type"
names(r8_data)[4]  <- "total_rate"
names(r8_data)[10] <- "fall_rate"
```

```{r filter-r8, eval=FALSE}
# Filter to top-level NAICS sectors, DAFW case type only.
# Using the broadest NAICS code (e.g. "31-33" not "311") ensures we get
# the full sector average rather than a sub-industry figure.
mfg <- r8_data %>% filter(naics == "31-33", case_type == "DAFW")
fin <- r8_data %>% filter(naics == "52",    case_type == "DAFW")
pro <- r8_data %>% filter(naics == "54",    case_type == "DAFW")

# as.numeric() converts from character type (a side effect of col_names = FALSE).
# Suppressed cells shown as "-" in the BLS table will become NA here.
mfg_total <- as.numeric(mfg$total_rate[1])
mfg_falls <- as.numeric(mfg$fall_rate[1])
fin_total  <- as.numeric(fin$total_rate[1])
fin_falls  <- as.numeric(fin$fall_rate[1])
pro_total  <- as.numeric(pro$total_rate[1])
pro_falls  <- as.numeric(pro$fall_rate[1])

# Derived measure: falls as a percentage of all nonfatal injuries per sector
mfg_fall_share <- round(mfg_falls / mfg_total * 100, 1)
fin_fall_share  <- round(fin_falls  / fin_total  * 100, 1)
pro_fall_share  <- round(pro_falls  / pro_total  * 100, 1)
```

```{r clean-fatal, eval=FALSE}
# Convert to data frame for row-based indexing
fatal_df <- as.data.frame(fatal)

# Row positions verified from raw file inspection:
# Row 143 = Manufacturing (NAICS 31-33)
# Row 453 = Finance and insurance (NAICS 52)
# Row 488 = Professional, scientific, and technical services (NAICS 54)
mfg_fatal_total <- as.numeric(fatal_df[143, 3])
mfg_fatal_falls <- as.numeric(fatal_df[143, 7])
fin_fatal_total <- as.numeric(fatal_df[453, 3])
fin_fatal_falls <- as.numeric(fatal_df[453, 7])
pro_fatal_total <- as.numeric(fatal_df[488, 3])
pro_fatal_falls <- as.numeric(fatal_df[488, 7])

#Fatal injury counts were taken directly from CFOI Table A-1. Fall share of deaths are calculated by dividing fatal falls by total sector deaths.
mfg_fall_pct <- round(mfg_fatal_falls / mfg_fatal_total * 100, 1)
fin_fall_pct  <- round(fin_fatal_falls  / fin_fatal_total  * 100, 1)
pro_fall_pct  <- round(pro_fatal_falls  / pro_fatal_total  * 100, 1)
```